\bf On semidefinite-representable sets over valuation fields

### 2024-11-29 article/paper_padic_spec.tex
commit by Simone

\begin{theorem}
Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
\end{theorem}
\begin{proof}
  Let $C = C_1 \times \cdots \times C_n \subset K^n$ be as in \Cref{def_annuli},
  for some annuli $C_1,\ldots,C_n \subset K$. We claim that each $C_i$ is a spectrahedral
  shadow of height $1$ and degree $4$. Assume $C_i = \{x \in K : a_i \leq \val(x) \leq b_i\}$
  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron

  %%% ARRIVATO QUI
  $S_M \subset K^2$ defined by
  $$
  S_M= \left\{(x,y) \in K^2 : M(x,y) := \diag\left(\pi^ax, \pi^{-b}y, \begin{bmatrix} \pi^{-1} & -\pi^{-1}x \\ \pi^{-1}y & - \pi^{-1}  \\ \end{bmatrix}\right) \succeq 0\right\}.
  $$
We claim that $x \in A$ if and only if there exists $y \in K$ such that $(x,y) \in S_M$.

Let $x,y \in K$. By \Cref{caracsdp}, $M(x,y) \succeq 0$ if and only if $(x,y)$ is a solution of
\eqref{eq:annulussyst}:
\begin{equation}
  \label[type]{eq:annulussyst}
\begin{cases}
  \val(\pi^ax) \ge 0 \\
  \val(\pi^{-b}y) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( xy-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
		\val\left(x\right)\ge a\\
		\val\left(y\right)\ge -b\\
		\val\left( xy-1 \right) \ge 2
	\end{cases}
\end{equation}
Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$. The last inequality implies that $\val\left(x\right)+\val\left(y\right)=\val\left(xy\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x\right)=-\val\left(y\right)\le -(-b)  =b$, so $x \in C$. 
Reciprocally if $x \in C$ then $(x,x^{-1}) $ is a solution of \eqref{eq:annulussyst}.
\end{proof}

>>>>

\begin{theorem}
Polyannuli in $K^n$ are spectrahedral shadows with height $m=n$ and degree $d=4n$.
\end{theorem}
\begin{proof}
  Let $C = C_1 \times \cdots \times C_n \subset K^n$ be as in \Cref{def_annuli},
  for some annuli $C_1,\ldots,C_n \subset K$. We claim that each $C_i$ is a spectrahedral
  shadow of height $1$ and degree $4$. Assume $C_i = \{x_i \in K : a_i \leq \val(x_i) \leq b_i\}$
  for some $a_i, b_i \in \R^*_+$ with $a_i < b_i$. Consider the spectrahedron
  $S_{M^{(i)}} \subset K^2$ defined by
  $$
  S_{M^{(i)}} = \left\{(x_i,y_i) \in K^2 :
  M^{(i)}(x_i,y_i) := \diag\left(\pi^a x_i, \pi^{-b} y_i,
  \begin{bmatrix}
    \pi^{-1} & -\pi^{-1} x_i  \\
    \pi^{-1} y_i & - \pi^{-1} \\
  \end{bmatrix}\right) \succeq 0
  \right\}.
  $$
  We claim that $x_i \in C_i$ if and only if there exists $y_i \in K$ such that $(x_i,y_i) \in S_{M^{(i)}}$.
  Indeed, by \Cref{caracsdp}, $M^{(i)}(x_i,y_i) \succeq 0$ if and only if $(x_i,y_i)$ is a solution of the system
  of inequalities:
  \begin{equation}
    \label[type]{eq:annulussyst}
    \begin{cases}
      \val(\pi^a x_i) \ge 0 \\
  \val(\pi^{-b} y_i) \ge 0\\
  \val(\pi^{-1}- \pi^{-1}) = +\infty \ge 0\\
  \val(\pi^{-2}\left( x_iy_i-1 \right))  \ge 0 
\end{cases}
\iff	
\begin{cases} 
  \val\left(x_i\right)\ge a\\
  \val\left(y_i\right)\ge -b\\
  \val\left(x_iy_i-1 \right) \ge 2
\end{cases}
\end{equation}
  %Therefore, if $(x, y)$ verifies \eqref{eq:annulussyst} then $\val\left(x\right)\ge a$, $\val\left(y\right)\ge -b$ and $ \left( xy-1 \right) \ge 2$.
  The last inequality implies that $\val\left(x_i\right)+\val\left(y_i\right)=\val\left(x_iy_i\right) = \val\left(-1\right) =0$ and therefore that $\val\left(x_i\right)=-\val\left(y_i\right)\le -(-b) = b$, so $x_i \in C_i$. 
Reciprocally if $x_i \in C_i$ then $(x_i,x_i^{-1})$ is a solution of \eqref{eq:annulussyst}.
This proves our claim.
Finally, since $C = C_1 \times \cdots \times C_n$, one has
\begin{equation*}
  \begin{aligned}
    C &=
    \{x=(x_1,\ldots,x_n) \in K^n : \exists y = (y_1,\ldots,y_n) \in K^n, (x_i,y_i) \in S_{M^{(i)}}, i=1,\ldots,n\} \\
    &= \{x \in K^n : \exists y \in K^n, (x,y) \in S_M\}
  \end{aligned}
\end{equation*}
with $S_M = \diag\left(M^{(1)}, M^{(2)}, \ldots, M^{(n)}\right) \in K[x,y]^{4n \times 4n}.$
\end{proof}
